Netbenchmark
========================================================

In the last decade, a great number of methods for
inferring gene regulatory networks from expression data have been proposed.

Several papers have compared and evaluated the different network inference methods relying on a simulated data. However, no publication so far has given comparison results on multiple and diverse datasets nor provided tools to fully reproduce (and possibly extend) the evaluation. 

We propose a systematic evaluation of network inference methods based on a benchmark of several simulated expression data.
This package allows replication this comparison between the different networks inference algorithms with only one line of code. 

```{r}
## Not run:
library(netbenchmark)
# To generate results of the main study:
# top20.aupr <- netbenchmark(methods="all",local.noise=20,global.noise=10,noiseType=c("normal","lognormal"),seed=1108) 
# To generate results of the noise study:
# noise.aupr <- noise.bench(methods="all",local.noise=seq(0,100,l=5),datasets.num=10,seed=2629)
# To generate results of the number of experiments study:
# experiments.aupr <- experiments.bench(methods="all",experiments.num=c(20,50,200,800),datasets.num=10,seed=4677)
## End(Not run)
```

The package provides an easy way to compare new techniques with the state-of-the-art  ones and to make new different benchmarks in the future.

First, define the wrapper functions:
```{r}
Spermancor<-function(data){
  cor(data,method="spearman")
}

Pearsoncor<-function(data){
  cor(data,method="pearson")
}
```

Note that the wrapper function returns a matrix which is the weighted adjacency matrix of the network inferred by the algorithm and that their columns and rows are named.

Evaluate five times this two naive inference methods in syntren300 datasource:
```{r}
res<-netbenchmark(datasources.names="syntren300",methods=c("Spermancor","Pearsoncor"))
aupr<-res[[1]][,-(1:2)]
```
Plot the $AUPR_{20}$ results:
```{r fig.width=7, fig.height=6}
boxplot(aupr, main="Syntren300")
```